Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-04-25 doc/manuscript/manuscript.tex
Added a short summary document and a flochart for use in the summary document

Eighty unique lines were selected from each population which satisfied
these criteria, and each yield test was comprised of 40 RILs. Three
high-yielding check cultivars and the two parents of the respective
population were also included in each test. Yield check cultivars
Dunphy, Osage\citep{Osage}, and Roy were used in tests 1 and 2, while
Dunphy, Dilday, and N.C. Raleigh were used for tests 3 and 4. These
lines were selected to represent the estimated maturities of the RILs in
each test. The parents for tests 1 and 2 were cultivars LMN09-119 and
N09-09, and the parents for tests 3 and 4 were LMN09-19 and N13-47.

@@

Using the data follected from this season, further selections were done
to identify high-yielding lines from the four tests. This was done by
identifying the RILs with a yield within or above a least significant
difference (LSD) of the average yield of the checks for each test.
Further selection was done using the seed composition traits by
identifying the thirty RILs with the highest protein + oil content on a
dry basis from among the RILs which had passed the yield selection
threshold.

These thirty lines were then grouped into two new tests of 15 RILs each
on the basis of maturity date. These two new tests are named Test 1 and
Test 2. Yield check cultivars were again assigned to each test to match
the maturity dates of the RILs that were in each test. Cultivars Dunphy,
DIlday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis,
N10-697, and Osage were used as checks in Test 2.

>>>>

Eighty unique lines were selected from each population which satisfied
these criteria, and each yield test was comprised of 40 RILs. Three
high-yielding check cultivars and the two parents of the respective
population were also included in each test. Yield check cultivars
Dunphy, Osage\citep{Osage}, and Roy were used in tests 1 and 2, while
Dunphy, Dilday, and NC-Raleigh\citep{NCRaleighregistration} were used
for tests 3 and 4. These lines were selected to represent the estimated
maturities of the RILs in each test. The parents for tests 1 and 2 were
cultivars LMN09-119 and N09-09, and the parents for tests 3 and 4 were
LMN09-19 and N13-47.

@@

Using the data collected from the 2019 season season, further selections
were done to identify high-yielding lines from the four tests. This was
done by identifying the RILs with a yield within or above a least
significant difference (LSD) of the average yield of the checks for each
test. Further selection was done using the seed composition traits by
identifying the thirty RILs with the highest protein + oil content on a
dry basis from among the RILs which had passed the yield selection
threshold.

These thirty lines were then grouped into two new tests of 15 RILs each
based on maturity date. These two new tests are named Test 1 and Test 2.
Yield check cultivars were again assigned to each test to match the
maturity dates of the RILs that were in each test. Cultivars Dunphy,
DIlday, and NC-Raleigh were used as checks in Test 1 and Dunphy, Ellis,
N10-697, and Osage were used as checks in Test 2.
